Until further notice, all personnel should work from home if possible.  Work in the lab should be performed only if it cannot be done elsewhere.  In the event that you must work in the HEP lab (JH 174), including the clean room and general area, the following guidance is in effect.  This is in addition to safety and good scientific practices outlined in the general laboratory documentation.

\begin{itemize}
\item If you feel you are even slightly sick, whether your symptoms match COVID-19 or not, do not come to the lab.
\item Do not come to the lab unless you must. If work can be performed from home, you should do so.  If you are not sure, talk to your supervisor.
\item No more than 3 people are allowed in the lab at the same time.
\item Undergraduate and graduate students are not allowed to work in the lab alone.
\item If you decide that you need to come to the lab, you must do the following in advance:
    \begin{itemize}
    \item Add to the lab google calendar the day(s) and time window(s) you plan to be in the lab.  The title should be your name.  This must be done at least the day before you plan to go in.
    \item In addition, send email to all laboratory contacts (contact info at bottom) at least the day before of your plans to work in the lab and the following information:
    
    	    \begin{itemize}
	    	\item When you want to go in and for how long
		\item The reason you need to go in
	    \end{itemize}

	\item If your supervisor or one of the lab technicians tells you to not go to the lab, you must not go to the lab.
    \end{itemize}
\item To assist in maintaining a safe work place, the following items are available in the laboratory:
	\begin{itemize}
	\item gloves: available in several sizes
	\item masks: \textcolor{red}{check requirements}
	\item soap: \textcolor{red}{check, get some if needed}
	\item towels: \textcolor{red}{check, get some if needed}
	\item sanitizer: \textcolor{red}{check availability with university}
	\item wipes: \textcolor{red}{check availability with university}
	\end{itemize}
\newpage
\item While working in the lab, the following practices must be followed for everyone's safety:
	\begin{itemize}
		\item Wash your hands with soap immediately upon entering and just before exiting the laboratory.  Do this every time you enter or leave the laboratory.
		\item Practice social distancing whenever possible.  Ideally, you should work at least 10 feet apart from another person.
		\item A mask must be properly worn at all times when working in the lab if not alone.
		\item Wear disposable gloves when permitted by the work you're doing.  Remember, gloves must be worn in the clean room at all times.
		\item After you are done working in a space or when you leave the laboratory for the day, use a disinfectant spray or wipes to 	clean all surfaces that you touched including the bench top, tools, keyboard, your custom-made equipment, your chair, etc.
		\item Wipe the door handles before you leave the lab.
		\item Please dispose of whatever refuse you produce.
	\end{itemize}
\end{itemize}

If you have questions, please ask. 

Contact information for the laboratory contacts is below.

\begin{itemize}
\item Caleb Fangmeier
	\begin{itemize}
	\item email: \href{mailto:cfangmeier74@gmail.com}{cfangmeier74@gmail.com}
	\item phone: 
	\end{itemize}
\item Frank Golf
	\begin{itemize}
	\item email: \href{mailto:fgolf@unl.edu}{fgolf@unl.edu}
	\item phone: (858) 395 6869
	\end{itemize}
\item Ilya Kravchenko
	\begin{itemize}
	\item email: \href{mailto:ikrav@unl.edu}{ikrav@unl.edu}
	\item phone: 
	\end{itemize}	
\end{itemize}